---
title: "Study 2: Analysis"
author: "Emily Pohl"
format: docx
editor: visual
---

```{r}
rm(list = ls())
```

Packages

```{r}
library(haven)
library(dplyr)
library(psych)
library(ggplot2)
library(parameters)
library(interactions)
library(dplyr)
library(psych)
library(ltm) 
library(rstatix) 
library(car) 
library(ggplot2)
library(haven)
library(tidyr)
library(grid)
library(broom)
library(apaTables)
library(effectsize) 
library(lavaan)
library(semTools)
library(modsem)
```

```{r}
renv::init()
```


# Paper 2

```{r}
data_raw <- read_sav("../data/data_raw/data_raw_study2.sav")
n0 <- nrow(data_raw)
data_clean <- data_raw
```

# Data preparation

Exclusion criteria applied: no Taiwanese teachers, not finishing the questionnaire, failing at least 2/3 attention checks, no working experience at a primary or secondary school, previous work experience as a teacher

data_clean \<- data_clean %\>% filter(LANGUAGE != "nan" \| is.na(LANGUAGE)) n4 \<- nrow(data_clean) cat("After LANGUAGE filter:", n4, "rows (dropped", n3 - n4, ")\n")

```{r}
n0 <- nrow(data_clean)

data_clean <- data_clean %>%
  filter(!(AT_fail_sum %in% c(2, 3)) | is.na(AT_fail_sum))
n1 <- nrow(data_clean)
cat("After AT_fail_sum filter:", n1, "rows (dropped", n0 - n1, ")\n")

data_clean <- data_clean %>%
  filter(!(clean_schooltype %in% c(1, 2, 3, 4)))
n2 <- nrow(data_clean)
cat("After clean_schooltype filter:", n2, "rows (dropped", n1 - n2, ")\n")

data_clean <- data_clean %>%
  filter(currentwork != 4 | is.na(currentwork))
n3 <- nrow(data_clean)
cat("After currentwork filter:", n3, "rows (dropped", n2 - n3, ")\n")

data_clean <- data_clean %>%
  filter(LANGUAGE != "nan" | is.na(LANGUAGE))
n4 <- nrow(data_clean)
cat("After LANGUAGE filter:", n4, "rows (dropped", n3 - n4, ")\n") 

nrow(data_raw)
nrow(data_clean) 
```

```{r}
write_sav(
  data_clean,
  "../data/data_clean/data_clean_study2.sav"
)
```

Data Cleaning and Preparation Scale Composition

```{r}

data_clean$EmEx <- rowMeans(data_clean[, paste0("emex", 1:9)], na.rm = TRUE)
data_clean$Dep <- rowMeans(data_clean[, paste0("dep", 1:5)], na.rm = TRUE)

data_clean$Anger <- rowMeans(data_clean[, c("anger_intense", "anger_frequent")], na.rm = TRUE)
data_clean$Anxiety <- rowMeans(data_clean[, c("anxiety_intense", "anxiety_frequent")], na.rm = TRUE)
data_clean$Shame <- rowMeans(data_clean[, c("shame_intense", "shame_frequent")], na.rm = TRUE)
data_clean$Joy <- rowMeans(data_clean[, c("joy_intense", "joy_frequent")], na.rm = TRUE) 
data_clean$Pride <- rowMeans(data_clean[, c("pride_intense", "pride_frequent")], na.rm = TRUE)

data_clean$NegApp <- rowMeans(data_clean[, c("anger_intense", "anger_frequent", "anxiety_intense", "anxiety_frequent", "shame_intense", "shame_frequent")], na.rm = TRUE)

data_clean$HideAnger <- rowMeans(data_clean[, c("anger_suppress", "anger_hide")], na.rm = TRUE)
data_clean$HideAnxiety <- rowMeans(data_clean[, c("anxiety_suppress", "anxiety_hide")], na.rm = TRUE)
data_clean$HideShame <- rowMeans(data_clean[, c("shame_suppress", "shame_hide")], na.rm = TRUE)
data_clean$FakeJoy <- rowMeans(data_clean[, c("joy_fake")], na.rm = TRUE)
data_clean$FakePride <- rowMeans(data_clean[, c("pride_fake")], na.rm = TRUE)


data_clean$ReappAnger <- rowMeans(data_clean[, c("reg_anger_reapp1", "reg_anger_reapp2")], na.rm = TRUE)
data_clean$ReappAnxiety <- rowMeans(data_clean[, c("reg_anxiety_reapp1", "reg_anxiety_reapp2")], na.rm = TRUE)
data_clean$ReappShame <- rowMeans(data_clean[, c("reg_shame_reapp1", "reg_shame_reapp2")], na.rm = TRUE)

data_clean$HideNeg <- rowMeans(data_clean[, c("anger_suppress", "anger_hide", "anxiety_suppress", "anxiety_hide", "shame_suppress", "shame_hide")], na.rm = TRUE)

```

Reliability for habitual emotional experiences

Joy (alpha = .767)

```{r}
Rel_Joy <- data_clean[, c("joy_intense", "joy_frequent")]
psych::alpha(Rel_Joy)
```

Anger (alpha = .770)

```{r}
Rel_Anger <- data_clean[, c("anger_intense", "anger_frequent")]
psych::alpha(Rel_Anger)
```

Anxiety (alpha = .893)

```{r}
Rel_Anxiety <- data_clean[, c("anxiety_intense", "anxiety_frequent")]
psych::alpha(Rel_Anxiety)
```

Shame (alpha = .882)

```{r}
Rel_Shame <- data_clean[, c("shame_intense", "shame_frequent")]
psych::alpha(Rel_Shame)
```

Hide Anger a = .817

```{r}
Rel_HideAnger <- data_clean[, c("anger_suppress", "anger_hide")]
psych::alpha(Rel_HideAnger)
```

Hide Anxiety a = .828

```{r}
Rel_HideAnxiety <- data_clean[, c("anxiety_suppress", "anxiety_hide")]
psych::alpha(Rel_HideAnxiety)
```

Hide Shame a = .882

```{r}
Rel_HideShame <- data_clean[, c("shame_intense", "shame_frequent")]
psych::alpha(Rel_HideShame)
```

Emotional Exhaustion a = .941

```{r}
Rel_EmEx <- data_clean %>% select(emex1:emex9)
psych::alpha(Rel_EmEx)
```

Depersonalization: a = .861

```{r}
Rel_Dep <- data_clean %>% select(dep1:dep5)
psych::alpha(Rel_Dep)
```

# Descriptives

```{r}

data_clean$age_real <- data_clean$age + 19
describe(data_clean$age_real)

table(data_clean$LANGUAGE)

describe(data_clean$EmEx)
describe(data_clean$Dep)

describe(data_clean$Joy)
describe(data_clean$Pride)
describe(data_clean$Anger)
describe(data_clean$Anxiety)
describe(data_clean$Shame)

describe(data_clean$HideAnger)
describe(data_clean$HideAnxiety)
describe(data_clean$HideShame)
describe(data_clean$FakeJoy)

describe(data_clean$TeachExp)
data_clean$gender <- as.factor(data_clean$gender)
gender_table <- table(data_clean$gender)
print(gender_table)
```

```{r}
vars <- data_clean[, c("Joy","Pride","Anger","Anxiety","Shame",
                       "HideAnger","HideAnxiety","HideShame",
                       "FakeJoy","EmEx","Dep","TeachExp","age_real")]


describe(vars) %>%
  select(mean, sd, min, max) %>%
  round(2)
```

```{r}
cor.data_clean <- data_clean %>% dplyr::select("anger_frequent", "anger_intense", "anxiety_frequent", "anxiety_intense", "joy_frequent", "joy_intense", "shame_frequent", "shame_intense") 
cor(cor.data_clean) 
cor(cor.data_clean,use = "pairwise.complete.obs") 


apa.cor.table(cor.data_clean, landscape = F, filename = "Correlation_2026_03_06.rtf")
```

# Correlation Analysis

```{r}

cor.data_clean <- data_clean %>% dplyr::select("EmEx", "Dep", 
                                       "Anger", "Anxiety",  
                                       "Joy", 
                                       "HideAnger", "HideAnxiety",
                                       "FakeJoy",
                                       "TeachExp") 
cor(cor.data_clean) 
cor(cor.data_clean,use = "pairwise.complete.obs") 


apa.cor.table(cor.data_clean, landscape = F, filename = "Correlation.ManyTeachers.March.rtf")
```

# Hypotheses

# Replication and Extension

## Model 1: Emotional Exhaustion

```{r}
model_manyteachers_emex_sem <- "
MI_EmEx       =~ emex1 + emex2 + emex3 + emex4 + emex5 + emex6 + emex7 + emex8 + emex9
MI_Anger      =~ anger_intense + anger_frequent
MI_Anxiety    =~ anxiety_intense + anxiety_frequent
MI_Joy        =~ joy_intense + joy_frequent 

MI_EmEx ~ MI_Anger + MI_Anxiety + MI_Joy + gender_factor + TeachExp

"

fit_manyteachers_EmEx <- sem(model_manyteachers_emex_sem, data = data_clean)
summary(fit_manyteachers_EmEx, fit.measures = TRUE, standardized = TRUE, rsquare = TRUE)

```

```{r}
parameterEstimates(fit_manyteachers_EmEx, standardized = TRUE, ci = TRUE)
```

## Model 2: Depersonalization

```{r}
model_manyteachers_dep_sem <- "
MI_Dep        =~ dep1 + dep2 + dep3 + dep4 + dep5
MI_Anger      =~ anger_intense + anger_frequent
MI_Anxiety    =~ anxiety_intense + anxiety_frequent
MI_Joy        =~ joy_intense + joy_frequent 

MI_Dep ~ MI_Anger + MI_Anxiety + MI_Joy + gender_factor + TeachExp

"

fit_manyteachers_dep <- sem(model_manyteachers_dep_sem, data = data_clean)

summary(fit_manyteachers_dep, fit.measures = TRUE, standardized = TRUE, rsquare = TRUE)

```

```{r}
parameterEstimates(fit_manyteachers_dep, standardized = TRUE, ci = TRUE)
```

# Emotion \* Emotional Labor =\> Burnout

## Emotional Exhaustion

### Model 1: Anger

```{r}
model_sem_1a <- '
MI_EmEx       =~ emex1 + emex2 + emex3 + emex4 + emex5 + emex6 + emex7 + emex8 + emex9
MI_Anger     =~ anger_intense + anger_frequent
MI_HideAnger =~ anger_suppress + anger_hide

MI_EmEx ~ MI_Anger + MI_HideAnger + MI_Anger:MI_HideAnger
'

fit_1a <- modsem(model_sem_1a, data = data_clean)
summary(fit_1a, standardized = TRUE) 
```

```{r}
# Coefficients from your modsem output
b0 <- 0                 # intercept / latent mean (centered)
b_anger <- 0.467        # beta for MI_Anger (now moderator)
b_hide <- 0.323         # beta for MI_HideAnger (now predictor on x-axis)
b_interaction <- 0.074  # beta for interaction MI_Anger:MI_HideAnger

# Optional standard errors for CIs (from summary(fit_1a))
SE_b0 <- 0
SE_anger <- 0.062
SE_hide <- 0.053
SE_interaction <- 0.033

# Create a dataframe for plotting
plot_data <- expand.grid(
  MI_HideAnger = seq(-2, 2, by = 0.1),   # x-axis predictor
  MI_Anger = c(-1, 0, 1)                 # moderator at low, mean, high
)

# Calculate predicted MI_EmEx
plot_data$MI_EmEx <- with(plot_data,
                          b0 + b_hide*MI_HideAnger + b_anger*MI_Anger +
                            b_interaction*MI_HideAnger*MI_Anger)

# Approximate SE for predicted values (optional)
plot_data$SE_pred <- with(plot_data, sqrt(
  SE_b0^2 +
    (SE_hide * MI_HideAnger)^2 +
    (SE_anger * MI_Anger)^2 +
    (SE_interaction * MI_HideAnger * MI_Anger)^2
))

# Confidence intervals
plot_data$lower <- plot_data$MI_EmEx - 1.96*plot_data$SE_pred
plot_data$upper <- plot_data$MI_EmEx + 1.96*plot_data$SE_pred

# Plot
plotMI <- ggplot(plot_data, aes(x = MI_HideAnger, y = MI_EmEx,
                                color = factor(MI_Anger),
                                linetype = factor(MI_Anger),
                                group = MI_Anger)) +
  geom_line() +
  geom_ribbon(aes(ymin = lower, ymax = upper), fill = "gray50", alpha = 0.05, color = NA) +
  scale_linetype_manual(values = c("dotted", "dashed", "solid"),
                        labels = c("Low", "Mean", "High")) +
  scale_color_manual(values = c("#000000", "#000000", "#000000"),
                     labels = c("Low", "Mean", "High")) +
  labs(x = "MI_HideAnger", y = "Predicted MI_EmEx",
       title = "Interaction Effect: MI_HideAnger × MI_Anger",
       color = "MI_Anger Level",
       linetype = "MI_Anger Level") +
  theme_minimal() +
  coord_cartesian(ylim = c(-2, 2)) +
  theme(legend.position = "bottom",
        legend.title = element_text(face = "bold"),
        legend.text = element_text(size = 10))

# Display the plot
plotMI
```

```{r}
# Coefficients from modsem output
b0 <- 0
b_anger <- 0.467
b_hide <- 0.323
b_interaction <- 0.074

# Optional standard errors for approximate CIs
SE_b0 <- 0
SE_anger <- 0.062
SE_hide <- 0.053
SE_interaction <- 0.033

# Create dataframe for plotting
plot_data <- expand.grid(
  MI_HideAnger = seq(-2, 2, by = 0.1),
  MI_Anger = c(-1, 0, 1)
)

# Predicted values
plot_data$MI_EmEx <- with(
  plot_data,
  b0 + b_hide * MI_HideAnger + b_anger * MI_Anger +
    b_interaction * MI_HideAnger * MI_Anger
)

# Approximate SE for predicted values
plot_data$SE_pred <- with(plot_data, sqrt(
  SE_b0^2 +
    (SE_hide * MI_HideAnger)^2 +
    (SE_anger * MI_Anger)^2 +
    (SE_interaction * MI_HideAnger * MI_Anger)^2
))

# Confidence intervals
plot_data$lower <- plot_data$MI_EmEx - 1.96 * plot_data$SE_pred
plot_data$upper <- plot_data$MI_EmEx + 1.96 * plot_data$SE_pred

# Recode moderator labels
plot_data$Anger_Level <- factor(
  plot_data$MI_Anger,
  levels = c(-1, 0, 1),
  labels = c("Low", "Medium", "High")
)

# Plot
plotMI <- ggplot(
  plot_data,
  aes(
    x = MI_HideAnger,
    y = MI_EmEx,
    linetype = Anger_Level,
    group = Anger_Level
  )
) +
  geom_ribbon(
    aes(ymin = lower, ymax = upper),
    fill = "grey50",
    alpha = 0.08,
    color = NA
  ) +
  geom_line(color = "black", linewidth = 0.8) +
  scale_linetype_manual(
    values = c("dotted", "dashed", "solid"),
    name = "Anger",
    labels = c("Low", "Medium", "High")
  ) +
  labs(
    x = "Hiding Anger",
    y = "Emotional Exhaustion"
  ) +
  coord_cartesian(ylim = c(-2, 2)) +
  theme_minimal(base_family = "Times New Roman") +
  theme(
    plot.title = element_blank(),
    panel.grid.minor = element_blank(),
    panel.grid.major = element_line(linewidth = 0.2),
    axis.line = element_line(color = "black", linewidth = 0.3),
    legend.position = "bottom",
    legend.title = element_text(face = "bold", size = 12),
    legend.text = element_text(size = 11),
    axis.title = element_text(size = 12),
    axis.text = element_text(size = 11),
    legend.key.width = unit(2.2, "cm"),
    legend.key.height = unit(0.7, "cm")
  )

plotMI
```

### Model 2: Anxiety

```{r}
model_sem_2a <- '
MI_EmEx       =~ emex1 + emex2 + emex3 + emex4 + emex5 + emex6 + emex7 + emex8 + emex9
MI_Anxiety     =~ anxiety_intense + anxiety_frequent
MI_HideAnxiety =~ anxiety_suppress + anxiety_hide

 MI_EmEx ~ MI_Anxiety + MI_HideAnxiety + MI_Anxiety:MI_HideAnxiety
'

fit_2a <- modsem(model_sem_2a , data = data_clean)
summary(fit_2a, standardized = TRUE)
```

### Model 3: Shame

```{r}
model_sem_3a <- '
MI_EmEx       =~ emex1 + emex2 + emex3 + emex4 + emex5 + emex6 + emex7 + emex8 + emex9
MI_Shame     =~ shame_intense + shame_frequent
MI_HideShame =~ shame_suppress + shame_hide

 MI_EmEx ~ MI_Shame + MI_HideShame + MI_Shame:MI_HideShame
'

fit_3a <- modsem(model_sem_3a , data = data_clean)
summary(fit_3a)
```

### Model 4: Joy

```{r}
model_sem_4a <- '

MI_EmEx =~ emex1 + emex2 + emex3 + emex4 + emex5 + emex6 + emex7 + emex8 + emex9
MI_Joy =~ joy_intense + joy_frequent

MI_EmEx ~ MI_Joy + joy_fake + MI_Joy:joy_fake
'
fit_4a <- modsem(model_sem_4a,
                 data = data_clean,
                 res.cov.method = "none")

summary(fit_4a, standardized = TRUE)
```

## Depersonalization

### Model 1: Anger

```{r}
model_sem_1b <- '
MI_Dep       =~ dep1 + dep2 + dep3 + dep4 + dep5
MI_Anger     =~ anger_intense + anger_frequent
MI_HideAnger =~ anger_suppress + anger_hide

 MI_Dep ~ MI_Anger + MI_HideAnger + MI_Anger:MI_HideAnger
'

fit_1b <- modsem(model_sem_1b, data = data_clean)
summary(fit_1b, standardized = TRUE)
```

```{r}
# Coefficients from your modsem output
b0 <- 0                  # intercept / latent mean (centered)
b_anger <- 0.476         # beta for MI_Anger (moderator)
b_hide <- 0.087          # beta for MI_HideAnger (predictor on x-axis)
b_interaction <- 0.080   # beta for interaction MI_Anger:MI_HideAnger

# Standard errors from modsem output
SE_b0 <- 0
SE_anger <- 0.062
SE_hide <- 0.044
SE_interaction <- 0.032

# Create dataframe for plotting
plot_data <- expand.grid(
  MI_HideAnger = seq(-2, 2, by = 0.1),   # x-axis predictor
  MI_Anger = c(-1, 0, 1)                 # moderator at low, mean, high
)

# Calculate predicted MI_Dep
plot_data$MI_Dep <- with(
  plot_data,
  b0 + b_hide * MI_HideAnger +
    b_anger * MI_Anger +
    b_interaction * MI_HideAnger * MI_Anger
)

# Approximate SE for predicted values
plot_data$SE_pred <- with(plot_data, sqrt(
  SE_b0^2 +
    (SE_hide * MI_HideAnger)^2 +
    (SE_anger * MI_Anger)^2 +
    (SE_interaction * MI_HideAnger * MI_Anger)^2
))

# Confidence intervals
plot_data$lower <- plot_data$MI_Dep - 1.96 * plot_data$SE_pred
plot_data$upper <- plot_data$MI_Dep + 1.96 * plot_data$SE_pred

# Plot
plotMI_dep <- ggplot(
  plot_data,
  aes(
    x = MI_HideAnger,
    y = MI_Dep,
    color = factor(MI_Anger),
    linetype = factor(MI_Anger),
    group = MI_Anger
  )
) +
  geom_line() +
  geom_ribbon(
    aes(ymin = lower, ymax = upper),
    fill = "gray50",
    alpha = 0.05,
    color = NA
  ) +
  scale_linetype_manual(
    values = c("longdash", "dotted", "solid"),
    labels = c("Low", "Mean", "High")
  ) +
  scale_color_manual(
    values = c("#000000", "#000000", "#000000"),
    labels = c("Low", "Mean", "High")
  ) +
  labs(
    x = "MI_HideAnger",
    y = "Predicted MI_Dep",
    title = "Interaction Effect: MI_HideAnger × MI_Anger on MI_Dep",
    color = "MI_Anger Level",
    linetype = "MI_Anger Level"
  ) +
  theme_minimal() +
  coord_cartesian(ylim = c(-2, 2)) +
  theme(
    legend.position = "bottom",
    legend.title = element_text(face = "bold"),
    legend.text = element_text(size = 10)
  )

# Display plot
plotMI_dep
```

### Model 2: Anxiety

```{r}
model_sem_2b <- '
MI_Dep       =~ dep1 + dep2 + dep3 + dep4 + dep5
MI_Anxiety     =~ anxiety_intense + anxiety_frequent
MI_HideAnxiety =~ anxiety_suppress + anxiety_hide

 MI_Dep ~ MI_Anxiety + MI_HideAnxiety + MI_Anxiety:MI_HideAnxiety
'

fit_2b <- modsem(model_sem_2b , data = data_clean)
summary(fit_2b, standardized = TRUE)
```

### Model 3: Shame

```{r}
model_sem_3b <- '
MI_Dep       =~ dep1 + dep2 + dep3 + dep4 + dep5
MI_Shame     =~ shame_intense + shame_frequent
MI_HideShame =~ shame_suppress + shame_hide

 MI_Dep ~ MI_Shame + MI_HideShame + MI_Shame:MI_HideShame
'

fit_3b <- modsem(model_sem_3b , data = data_clean)
summary(fit_3b)
```

### Model 4: Joy

```{r}
model_sem_4b <- '
MI_Dep     =~ dep1 + dep2 + dep3 + dep4 + dep5
MI_Joy     =~ joy_intense + joy_frequent
MI_FakeJoy =~ joy_fake

MI_Dep ~ MI_Joy + joy_fake + MI_Joy:joy_fake
'
fit_4b <- modsem(model_sem_4b,
                 data = data_clean,
                 res.cov.method = "none")
                 
summary(fit_4b, standardized = TRUE)
```
