---
title: "03_Study 2_measurement invariance"
format: pdf
editor: visual
---

```{r}
rm(list = ls())
```

# Measurement invariance: EmEx
### EmEx / Anger 

  anger_hide ~~ 0*anger_hide
```{r}
MI_modelH1a <- '
  MI_EmEx      =~ emex1 + emex2 + emex3 + emex4 + emex5 + emex6 + emex7 + emex8 + emex9

  MI_Anger     =~ 1*anger_intense + anger_frequent
  MI_Anger ~~ 1*MI_Anger

  MI_HideAnger =~ 1*anger_suppress + anger_hide
  MI_HideAnger ~~ 1*MI_HideAnger
'

fit_H1a <- cfa(MI_modelH1a,
            data = data_clean,
            group = "LANGUAGE")

inspect(fit_H1a, "converged")

summary(fit_H1a, fit.measures = TRUE)
fitMeasures(fit_H1a, c("cfi", "tli", "rmsea", "srmr"))


```
```{r}
fit_config <- cfa(
  MI_modelH1a,
  data  = data_clean,
  group = "LANGUAGE"
)

inspect(fit_config, "converged")
summary(fit_config, fit.measures = TRUE)


```
```{r}
fit_metric <- cfa(
  MI_modelH1a,
  data  = data_clean,
  group = "LANGUAGE",
  group.equal = "loadings"
)

inspect(fit_metric, "converged")
summary(fit_metric, fit.measures = TRUE)

```

```{r}
fit_scalar <- cfa(
  MI_modelH1a,
  data  = data_clean,
  group = "LANGUAGE",
  group.equal = c("loadings", "intercepts")
)
inspect(fit_scalar, "converged")
summary(fit_scalar, fit.measures = TRUE)
```

```{r}
fits <- list(
  config = fit_config,
  metric = fit_metric,
  scalar = fit_scalar
)

sapply(fits, function(x)
  fitMeasures(x, c("cfi","rmsea","srmr")))
```


```{r}

fitMeasures(fit_metric, "cfi") - fitMeasures(fit_config, "cfi")
fitMeasures(fit_scalar, "cfi") - fitMeasures(fit_metric, "cfi")

```


### EmEx / Anxiety
```{r}
MI_modelH2a <- '
  MI_EmEx      =~ emex1 + emex2 + emex3 + emex4 + emex5 + emex6 + emex7 + emex8 + emex9

  MI_Anxiety     =~ 1*anxiety_intense + anxiety_frequent
  MI_Anxiety ~~ 1*MI_Anxiety

  MI_HideAnxiety =~ 1*anxiety_suppress + anxiety_hide
  MI_HideAnxiety ~~ 1*MI_HideAnxiety
'

fit_anx <- cfa(MI_modelH2a,
            data = data_clean,
            group = "LANGUAGE")

inspect(fit_anx, "converged")

summary(fit_anx, fit.measures = TRUE)
fitMeasures(fit_anx, c("cfi", "tli", "rmsea", "srmr")) 

```


```{r}

fit_config <- cfa(
  MI_modelH2a,
  data  = data_clean,
  group = "LANGUAGE"
)

inspect(fit_config, "converged")
summary(fit_config, fit.measures = TRUE)


```
```{r}
fit_metric <- cfa(
  MI_modelH2a,
  data  = data_clean,
  group = "LANGUAGE",
  group.equal = "loadings"
)

inspect(fit_metric, "converged")
summary(fit_metric, fit.measures = TRUE)

```

```{r}
fit_scalar <- cfa(
  MI_modelH2a,
  data  = data_clean,
  group = "LANGUAGE",
  group.equal = c("loadings", "intercepts")
)
inspect(fit_scalar, "converged")
summary(fit_scalar, fit.measures = TRUE)
```

```{r}
fits <- list(
  config = fit_config,
  metric = fit_metric,
  scalar = fit_scalar
)

sapply(fits, function(x)
  fitMeasures(x, c("cfi","rmsea","srmr")))
```

```{r}

fitMeasures(fit_metric, "cfi") - fitMeasures(fit_config, "cfi")
fitMeasures(fit_scalar, "cfi") - fitMeasures(fit_metric, "cfi")

```
  shame_hide ~~ 0*shame_hide
### EmEx / Shame
```{r}
MI_modelH3a <- '
  MI_EmEx      =~ emex1 + emex2 + emex3 + emex4 + emex5 + emex6 + emex7 + emex8 + emex9

  MI_Shame     =~ 1*shame_intense + shame_frequent
  MI_Shame ~~ 1*MI_Shame

  MI_HideShame =~ 1*shame_suppress + shame_hide
  MI_HideShame ~~ 1*MI_HideShame
  
'



fit_shame <- cfa(MI_modelH3a,
            data = data_clean,
            group = "LANGUAGE")

inspect(fit_shame, "converged")

summary(fit_shame, fit.measures = TRUE)
fitMeasures(fit_shame, c("cfi", "tli", "rmsea", "srmr")) 

```


```{r}

fit_config <- cfa(
  MI_modelH3a,
  data  = data_clean,
  group = "LANGUAGE"
)

inspect(fit_config, "converged")
summary(fit_config, fit.measures = TRUE)


```
```{r}
fit_metric <- cfa(
  MI_modelH3a,
  data  = data_clean,
  group = "LANGUAGE",
  group.equal = "loadings"
)

inspect(fit_metric, "converged")
summary(fit_metric, fit.measures = TRUE)

```

```{r}
fit_scalar <- cfa(
  MI_modelH3a,
  data  = data_clean,
  group = "LANGUAGE",
  group.equal = c("loadings", "intercepts")
)
inspect(fit_scalar, "converged")
summary(fit_scalar, fit.measures = TRUE)
```

```{r}
fits <- list(
  config = fit_config,
  metric = fit_metric,
  scalar = fit_scalar
)

sapply(fits, function(x)
  fitMeasures(x, c("cfi","rmsea","srmr")))
```

```{r}

fitMeasures(fit_metric, "cfi") - fitMeasures(fit_config, "cfi")
fitMeasures(fit_scalar, "cfi") - fitMeasures(fit_metric, "cfi")

```

### EmEx / Joy
```{r}
MI_modelH4a <- '
  MI_EmEx      =~ emex1 + emex2 + emex3 + emex4 + emex5 + emex6 + emex7 + emex8 + emex9

  MI_Joy     =~ 1*joy_intense + joy_frequent
  MI_Joy ~~ 1*MI_Joy

  MI_FakeJoy =~ 1*joy_fake
   MI_FakeJoy ~~ 1* MI_FakeJoy
  
'



fit_joy <- cfa(MI_modelH4a,
            data = data_clean,
            group = "LANGUAGE")

inspect(fit_joy, "converged")

summary(fit_joy, fit.measures = TRUE)
fitMeasures(fit_joy, c("cfi", "tli", "rmsea", "srmr")) 

```


```{r}

fit_config <- cfa(
  MI_modelH4a,
  data  = data_clean,
  group = "LANGUAGE"
)

inspect(fit_config, "converged")
summary(fit_config, fit.measures = TRUE)


```
```{r}
fit_metric <- cfa(
  MI_modelH4a,
  data  = data_clean,
  group = "LANGUAGE",
  group.equal = "loadings"
)

inspect(fit_metric, "converged")
summary(fit_metric, fit.measures = TRUE)

```

```{r}
fit_scalar <- cfa(
  MI_modelH4a,
  data  = data_clean,
  group = "LANGUAGE",
  group.equal = c("loadings", "intercepts")
)
inspect(fit_scalar, "converged")
summary(fit_scalar, fit.measures = TRUE)
```

```{r}
fits <- list(
  config = fit_config,
  metric = fit_metric,
  scalar = fit_scalar
)

sapply(fits, function(x)
  fitMeasures(x, c("cfi","rmsea","srmr")))
```

```{r}

fitMeasures(fit_metric, "cfi") - fitMeasures(fit_config, "cfi")
fitMeasures(fit_scalar, "cfi") - fitMeasures(fit_metric, "cfi")

```


### EmEx / Pride
```{r}
MI_modelH5a <- '
  MI_EmEx      =~ emex1 + emex2 + emex3 + emex4 + emex5 + emex6 + emex7 + emex8 + emex9

  MI_Pride     =~ 1*pride_intense + pride_frequent
  MI_Pride ~~ 1*MI_Pride

  MI_FakePride =~ 1*pride_fake
   MI_FakePride ~~ 1*MI_FakePride
  
'



fit_joy <- cfa(MI_modelH5a,
            data = data_clean,
            group = "LANGUAGE")

inspect(fit_joy, "converged")

summary(fit_joy, fit.measures = TRUE)
fitMeasures(fit_joy, c("cfi", "tli", "rmsea", "srmr")) 

```


```{r}

fit_config <- cfa(
  MI_modelH5a,
  data  = data_clean,
  group = "LANGUAGE"
)

inspect(fit_config, "converged")
summary(fit_config, fit.measures = TRUE)


```
```{r}
fit_metric <- cfa(
  MI_modelH5a,
  data  = data_clean,
  group = "LANGUAGE",
  group.equal = "loadings"
)

inspect(fit_metric, "converged")
summary(fit_metric, fit.measures = TRUE)

```

```{r}
fit_scalar <- cfa(
  MI_modelH5a,
  data  = data_clean,
  group = "LANGUAGE",
  group.equal = c("loadings", "intercepts")
)
inspect(fit_scalar, "converged")
summary(fit_scalar, fit.measures = TRUE)
```

```{r}
fits <- list(
  config = fit_config,
  metric = fit_metric,
  scalar = fit_scalar
)

sapply(fits, function(x)
  fitMeasures(x, c("cfi","rmsea","srmr")))
```

```{r}

fitMeasures(fit_metric, "cfi") - fitMeasures(fit_config, "cfi")
fitMeasures(fit_scalar, "cfi") - fitMeasures(fit_metric, "cfi")

```

## Measurement Invariance: Dep

### Testing 05.02.26 --> *clean this up

```{r}
# Pakete
library(lavaan)
library(dplyr)
library(semTools)  # für lavTestScore()

# 0) Modelle (Dep vs. EE) – EE-Modell musst du ggf. anpassen (Items/Faktorname)

MI_modelH1b <- '

  MI_Dep =~ dep1 + dep2 + dep3 + dep4 + dep5

  MI_Anger =~ 1*anger_intense + anger_frequent

  MI_HideAnger =~ 1*anger_suppress + anger_hide
'


# 1) Configural
fit_config <- cfa(
  MI_modelH1b,
  data  = data_clean,
  group = "LANGUAGE",
  std.lv = FALSE  # marker-variable identification (default). Keep as is for now.
)

inspect(fit_config, "converged")
fitMeasures(fit_config, c("cfi","tli","rmsea","srmr"))

summary(fit_config, standardized = TRUE)


```

```{r}
fit_metric <- cfa(
  MI_modelH1b,
  data  = data_clean,
  group = "LANGUAGE",
  group.equal = c("loadings"),
  std.lv = FALSE
)

inspect(fit_metric, "converged")
fitMeasures(fit_metric, c("cfi","tli","rmsea","srmr"))

anova(fit_config, fit_metric)

```

```{r}
mi_metric <- modindices(fit_metric, sort = TRUE)

## Show only loading-related MIs (the "=~" operator)
subset(mi_metric,
       op == "=~" &
       lhs %in% c("MI_Dep") &
       rhs %in% c("dep1","dep2","dep3","dep4","dep5"))

head(mi_metric, 20)

```

```{r}
model_dep <- '
  MI_Dep =~ dep1 + dep2 + dep3 + dep4 + dep5
'

fit_dep_config <- cfa(model_dep, data = data_clean, group = "LANGUAGE")
fit_dep_metric <- cfa(model_dep, data = data_clean, group = "LANGUAGE",
                      group.equal = "loadings")

anova(fit_dep_config, fit_dep_metric)

fitMeasures(fit_dep_config, c("cfi","rmsea"))
fitMeasures(fit_dep_metric, c("cfi","rmsea"))

```

```{r}
mi_dep <- modindices(fit_dep_metric, sort = TRUE)

subset(mi_dep,
       op == "=~" &
       lhs == "MI_Dep")

```

```{r}
fit_dep_eng <- cfa(model_dep,
                   data = subset(data_clean, LANGUAGE == "eng"))

fit_dep_ger <- cfa(model_dep,
                   data = subset(data_clean, LANGUAGE == "ger"))

fitMeasures(fit_dep_eng, c("cfi","rmsea","srmr"))
fitMeasures(fit_dep_ger, c("cfi","rmsea","srmr"))

```
# Reliability Depersonalization per country

```{r}
dep_items <- c("dep1", "dep2", "dep3", "dep4", "dep5")

# --- Cronbach's alpha by group ---
alpha_eng <- psych::alpha(
  data_clean %>% filter(LANGUAGE == "eng") %>% select(all_of(dep_items)),
  check.keys = TRUE
)

alpha_ger <- psych::alpha(
  data_clean %>% filter(LANGUAGE == "ger") %>% select(all_of(dep_items)),
  check.keys = TRUE
)


```


# Partial invariance 

## Anger

```{r}
MI_modelH1b <- '
  MI_Dep =~ dep1 + dep2 + dep3 + dep4 + dep5

  MI_Anger     =~ anger_intense + anger_frequent
  MI_HideAnger =~ anger_suppress + anger_hide
'

# 1) Configural 
fit_H1b_config <- cfa(MI_modelH1b,
                      data = data_clean,
                      group = "LANGUAGE")

# 2) Metric
fit_H1b_metric <- cfa(MI_modelH1b,
                      data = data_clean,
                      group = "LANGUAGE",
                      group.equal = "loadings")

# 3) Partial metric (alle Ladungen gleich, außer dep5 auf MI_Dep)
fit_H1b_partial <- cfa(MI_modelH1b,
                       data = data_clean,
                       group = "LANGUAGE",
                       group.equal = "loadings",
                       group.partial = "MI_Dep=~dep5")

summary(fit_H1b_partial, fit.measures = TRUE)
fitMeasures(fit_H1b_partial, c("cfi","tli","rmsea","srmr"))

#  ΔCFI / ΔRMSEA
cbind(
  config = fitMeasures(fit_H1b_config, c("cfi","rmsea")),
  metric = fitMeasures(fit_H1b_metric, c("cfi","rmsea")),
  partial= fitMeasures(fit_H1b_partial, c("cfi","rmsea"))
)

anova(fit_H1b_config, fit_H1b_metric, fit_H1b_partial)

```

- partial metric invariance given! 

## Anxiety

```{r}
MI_modelH2b <- '
  MI_Dep =~ dep1 + dep2 + dep3 + dep4 + dep5

  MI_Anxiety =~ anxiety_intense + anxiety_frequent
  MI_HideAnxiety =~ c(h1, h2)*anxiety_suppress + c(h1, h2)*anxiety_hide
'

# 1) Configural 
fit_H2b_config <- cfa(MI_modelH2b,
                      data = data_clean,
                      group = "LANGUAGE")

# 2) Metric
fit_H2b_metric <- cfa(MI_modelH2b,
                      data = data_clean,
                      group = "LANGUAGE",
                      group.equal = "loadings")

# 3) Partial metric (alle Ladungen gleich, außer dep5 auf MI_Dep)
fit_H2b_partial <- cfa(MI_modelH2b,
                       data = data_clean,
                       group = "LANGUAGE",
                       group.equal = "loadings",
                       group.partial = "MI_Dep=~dep5")

summary(fit_H2b_partial, fit.measures = TRUE)
fitMeasures(fit_H2b_partial, c("cfi","tli","rmsea","srmr"))

#  ΔCFI / ΔRMSEA
cbind(
  config = fitMeasures(fit_H2b_config, c("cfi","rmsea")),
  metric = fitMeasures(fit_H2b_metric, c("cfi","rmsea")),
  partial= fitMeasures(fit_H2b_partial, c("cfi","rmsea"))
)

anova(fit_H2b_config, fit_H2b_metric, fit_H2b_partial)

```

-> metric invariance given! 

## Shame

```{r}
MI_modelH3b <- '
  MI_Dep =~ dep1 + dep2 + dep3 + dep4 + dep5

  MI_Shame     =~ shame_intense + shame_frequent
  MI_HideShame =~ shame_suppress + shame_hide
'

# 1) Configural 
fit_H3b_config <- cfa(MI_modelH3b,
                      data = data_clean,
                      group = "LANGUAGE")

# 2) Metric
fit_H3b_metric <- cfa(MI_modelH3b,
                      data = data_clean,
                      group = "LANGUAGE",
                      group.equal = "loadings")

# 3) Partial metric (alle Ladungen gleich, außer dep5 auf MI_Dep)
fit_H3b_partial <- cfa(MI_modelH3b,
                       data = data_clean,
                       group = "LANGUAGE",
                       group.equal = "loadings",
                       group.partial = "MI_Dep=~dep5")

summary(fit_H3b_partial, fit.measures = TRUE)
fitMeasures(fit_H3b_partial, c("cfi","tli","rmsea","srmr"))

#  ΔCFI / ΔRMSEA
cbind(
  config = fitMeasures(fit_H3b_config, c("cfi","rmsea")),
  metric = fitMeasures(fit_H3b_metric, c("cfi","rmsea")),
  partial= fitMeasures(fit_H3b_partial, c("cfi","rmsea"))
)

anova(fit_H3b_config, fit_H3b_metric, fit_H3b_partial)

```

-> partial metric invariance given

##Joy

```{r}
MI_modelH4b <- '
  MI_Dep =~ dep1 + dep2 + dep3 + dep4 + dep5

  MI_Joy     =~ joy_intense + joy_frequent
  MI_FakeJoy =~ joy_fake
'

# 1) Configural 
fit_H4b_config <- cfa(MI_modelH4b,
                      data = data_clean,
                      group = "LANGUAGE")

# 2) Metric
fit_H4b_metric <- cfa(MI_modelH4b,
                      data = data_clean,
                      group = "LANGUAGE",
                      group.equal = "loadings")

# 3) Partial metric (alle Ladungen gleich, außer dep5 auf MI_Dep)
fit_H4b_partial <- cfa(MI_modelH4b,
                       data = data_clean,
                       group = "LANGUAGE",
                       group.equal = "loadings",
                       group.partial = "MI_Dep=~dep5")

summary(fit_H4b_partial, fit.measures = TRUE)
fitMeasures(fit_H4b_partial, c("cfi","tli","rmsea","srmr"))

#  ΔCFI / ΔRMSEA
cbind(
  config = fitMeasures(fit_H4b_config, c("cfi","rmsea")),
  metric = fitMeasures(fit_H4b_metric, c("cfi","rmsea")),
  partial= fitMeasures(fit_H4b_partial, c("cfi","rmsea"))
)

anova(fit_H4b_config, fit_H4b_metric, fit_H4b_partial)

```

-> partial metric invariance given

### Dep / Anger
  anger_hide ~~ 0*anger_hide
```{r}
MI_modelH1b <- '
  MI_Dep      =~ dep1 + dep2 + dep3 + dep4 + dep5

  MI_Anger     =~ anger_intense + anger_frequent

  MI_HideAnger =~ anger_suppress + anger_hide
'

fit_H1b <- cfa(MI_modelH1b,
            data = data_clean,
            group = "LANGUAGE")

inspect(fit_H1b, "converged")

summary(fit_H1b, fit.measures = TRUE)
fitMeasures(fit_H1b, c("cfi", "tli", "rmsea", "srmr"))

modindices(fit_metric, sort = TRUE)

```

```{r}
library(lavaan)

fit_metric <- cfa(MI_modelH1b,
                  data = data_clean,
                  group = "LANGUAGE",
                  group.equal = "loadings")

anova(fit_H1b, fit_metric)

fit_partial <- cfa(MI_modelH1b,
                   data = data_clean,
                   group = "LANGUAGE",
                   group.equal = "loadings",
                   group.partial = "MI_Dep =~ dep5")

anova(fit_metric, fit_partial)


fitMeasures(fit_H1b, "cfi")
fitMeasures(fit_metric, "cfi")

subset(modindices(fit_metric),
       grepl("^dep", rhs))

```

```{r}
fit_config <- cfa(
  MI_modelH1b,
  data  = data_clean,
  group = "LANGUAGE"
)

inspect(fit_config, "converged")
summary(fit_config, fit.measures = TRUE)


```
```{r}
fit_metric <- cfa(
  MI_modelH1b,
  data  = data_clean,
  group = "LANGUAGE",
  group.equal = "loadings"
)

inspect(fit_metric, "converged")
summary(fit_metric, fit.measures = TRUE)

```

```{r}
fit_scalar <- cfa(
  MI_modelH1b,
  data  = data_clean,
  group = "LANGUAGE",
  group.equal = c("loadings", "intercepts")
)
inspect(fit_scalar, "converged")
summary(fit_scalar, fit.measures = TRUE)
```

```{r}
fits <- list(
  config = fit_config,
  metric = fit_metric,
  scalar = fit_scalar
)

sapply(fits, function(x)
  fitMeasures(x, c("cfi","rmsea","srmr")))
```


```{r}

fitMeasures(fit_metric, "cfi") - fitMeasures(fit_config, "cfi")
fitMeasures(fit_scalar, "cfi") - fitMeasures(fit_metric, "cfi")

```

### Dep / Anxiety
  anger_hide ~~ 0*anger_hide
```{r}
library(lavaan)
MI_modelH2b <- '
  MI_Dep      =~ dep1 + dep2 + dep3 + dep4 + dep5

  MI_Anxiety     =~ 1*anxiety_intense + anxiety_frequent
  MI_Anxiety ~~ 1*MI_Anxiety

  MI_HideAnxiety =~ 1*anxiety_suppress + anxiety_hide
  MI_HideAnxiety ~~ 1*MI_HideAnxiety

'

fit_H2b <- cfa(MI_modelH2b,
            data = data_clean,
            group = "LANGUAGE")

inspect(fit_H2b, "converged")

summary(fit_H2b, fit.measures = TRUE)
fitMeasures(fit_H2b, c("cfi", "tli", "rmsea", "srmr"))


```


```{r}
MI_modelH3b <- '
  MI_Dep      =~ dep1 + dep2 + dep3 + dep4

  MI_Anxiety     =~ 1*anxiety_intense + anxiety_frequent
  MI_Anxiety ~~ 1*MI_Anxiety

  MI_HideAnxiety =~ 1*anxiety_suppress + anxiety_hide
  MI_HideAnxiety ~~ 1*MI_HideAnxiety

'

fit_H3b <- cfa(MI_modelH3b,
            data = data_clean,
            group = "LANGUAGE")

inspect(fit_H3b, "converged")

summary(fit_H3b, fit.measures = TRUE)
fitMeasures(fit_H3b, c("cfi", "tli", "rmsea", "srmr"))


```



```{r}

fit_config <- cfa(
  MI_modelH2b,
  data  = data_clean,
  group = "LANGUAGE"
)

inspect(fit_config, "converged")
summary(fit_config, fit.measures = TRUE)
fit_metric <- cfa(
  MI_modelH2b,
  data  = data_clean,
  group = "LANGUAGE",
  group.equal = "loadings"
)

inspect(fit_metric, "converged")
summary(fit_metric, fit.measures = TRUE)

```


```{r}

fit_config <- cfa(
  MI_modelH3b,
  data  = data_clean,
  group = "LANGUAGE"
)

inspect(fit_config, "converged")
summary(fit_config, fit.measures = TRUE)

```




```{r}
fit_metric <- cfa(
  MI_modelH3b,
  data  = data_clean,
  group = "LANGUAGE",
  group.equal = "loadings"
)

inspect(fit_metric, "converged")
summary(fit_metric, fit.measures = TRUE)

```

```{r}
fit_scalar <- cfa(
  MI_modelH3b,
  data  = data_clean,
  group = "LANGUAGE",
  group.equal = c("loadings", "intercepts")
)
inspect(fit_scalar, "converged")
summary(fit_scalar, fit.measures = TRUE)
```

```{r}
fits <- list(
  config = fit_config,
  metric = fit_metric,
  scalar = fit_scalar
)

sapply(fits, function(x)
  fitMeasures(x, c("cfi","rmsea","srmr")))
```


```{r}

fitMeasures(fit_metric, "cfi") - fitMeasures(fit_config, "cfi")
fitMeasures(fit_scalar, "cfi") - fitMeasures(fit_metric, "cfi")

```

### Dep / Shame

```{r}
MI_modelH3b <- '
  MI_Dep      =~ dep1 + dep2 + dep3 + dep4 + dep5

  MI_Shame     =~ 1*shame_intense + shame_frequent
  MI_Shame ~~ 1*MI_Shame

  MI_HideShame =~ 1*shame_suppress + shame_hide
  MI_HideShame ~~ 1*MI_HideShame

'

fit_H3b <- cfa(MI_modelH3b,
            data = data_clean,
            group = "LANGUAGE")

inspect(fit_H3b, "converged")

summary(fit_H3b, fit.measures = TRUE)
fitMeasures(fit_H3b, c("cfi", "tli", "rmsea", "srmr"))


```
```{r}
fit_config <- cfa(
  MI_modelH3b,
  data  = data_clean,
  group = "LANGUAGE"
)

inspect(fit_config, "converged")
summary(fit_config, fit.measures = TRUE)


```
```{r}
fit_metric <- cfa(
  MI_modelH3b,
  data  = data_clean,
  group = "LANGUAGE",
  group.equal = "loadings"
)

inspect(fit_metric, "converged")
summary(fit_metric, fit.measures = TRUE)

```

```{r}
fit_scalar <- cfa(
  MI_modelH3b,
  data  = data_clean,
  group = "LANGUAGE",
  group.equal = c("loadings", "intercepts")
)
inspect(fit_scalar, "converged")
summary(fit_scalar, fit.measures = TRUE)
```

```{r}
fits <- list(
  config = fit_config,
  metric = fit_metric,
  scalar = fit_scalar
)

sapply(fits, function(x)
  fitMeasures(x, c("cfi","rmsea","srmr")))
```


```{r}

fitMeasures(fit_metric, "cfi") - fitMeasures(fit_config, "cfi")
fitMeasures(fit_scalar, "cfi") - fitMeasures(fit_metric, "cfi")

```


### Dep / Joy

```{r}
MI_modelH4b <- '
  MI_Dep      =~ dep1 + dep2 + dep3 + dep4 + dep5

  MI_Joy     =~ 1*joy_intense + joy_frequent
  MI_Joy ~~ 1*MI_Joy

  MI_FakeJoy =~ 1*joy_fake 
  MI_FakeJoy ~~ 1*MI_FakeJoy

'

fit_H4b <- cfa(MI_modelH4b,
            data = data_clean,
            group = "LANGUAGE")

inspect(fit_H4b, "converged")

summary(fit_H4b, fit.measures = TRUE)
fitMeasures(fit_H4b, c("cfi", "tli", "rmsea", "srmr"))


```
```{r}
fit_config <- cfa(
  MI_modelH4b,
  data  = data_clean,
  group = "LANGUAGE"
)

inspect(fit_config, "converged")
summary(fit_config, fit.measures = TRUE)


```
```{r}
fit_metric <- cfa(
  MI_modelH4b,
  data  = data_clean,
  group = "LANGUAGE",
  group.equal = "loadings"
)

inspect(fit_metric, "converged")
summary(fit_metric, fit.measures = TRUE)

```

```{r}
fit_scalar <- cfa(
  MI_modelH4b,
  data  = data_clean,
  group = "LANGUAGE",
  group.equal = c("loadings", "intercepts")
)
inspect(fit_scalar, "converged")
summary(fit_scalar, fit.measures = TRUE)
```

```{r}
fits <- list(
  config = fit_config,
  metric = fit_metric,
  scalar = fit_scalar
)

sapply(fits, function(x)
  fitMeasures(x, c("cfi","rmsea","srmr")))
```


```{r}

fitMeasures(fit_metric, "cfi") - fitMeasures(fit_config, "cfi")
fitMeasures(fit_scalar, "cfi") - fitMeasures(fit_metric, "cfi")

```


### Dep / Pride

```{r}
MI_modelH5b <- '
  MI_Dep      =~ dep1 + dep2 + dep3 + dep4 + dep5

  MI_Pride    =~ 1*pride_intense + pride_frequent
  MI_Pride ~~ 1*MI_Pride

  MI_FakePride =~ 1*pride_fake 
  MI_FakePride ~~ 1*MI_FakePride

'

fit_H5b <- cfa(MI_modelH5b,
            data = data_clean,
            group = "LANGUAGE")

inspect(fit_H5b, "converged")

summary(fit_H5b, fit.measures = TRUE)
fitMeasures(fit_H5b, c("cfi", "tli", "rmsea", "srmr"))


```
```{r}
fit_config <- cfa(
  MI_modelH5b,
  data  = data_clean,
  group = "LANGUAGE"
)

inspect(fit_config, "converged")
summary(fit_config, fit.measures = TRUE)


```
```{r}
fit_metric <- cfa(
  MI_modelH5b,
  data  = data_clean,
  group = "LANGUAGE",
  group.equal = "loadings"
)

inspect(fit_metric, "converged")
summary(fit_metric, fit.measures = TRUE)

```

```{r}
fit_scalar <- cfa(
  MI_modelH5b,
  data  = data_clean,
  group = "LANGUAGE",
  group.equal = c("loadings", "intercepts")
)
inspect(fit_scalar, "converged")
summary(fit_scalar, fit.measures = TRUE)
```

```{r}
fits <- list(
  config = fit_config,
  metric = fit_metric,
  scalar = fit_scalar
)

sapply(fits, function(x)
  fitMeasures(x, c("cfi","rmsea","srmr")))
```


```{r}

fitMeasures(fit_metric, "cfi") - fitMeasures(fit_config, "cfi")
fitMeasures(fit_scalar, "cfi") - fitMeasures(fit_metric, "cfi")

```

## Invariance only for EmEx 

```{r}

data_clean$LANGUAGE <- factor(
  data_clean$LANGUAGE,
  levels = c("ger", "eng", "nan")
)
str(data_clean$LANGUAGE)

model_EmEx <- '
  EmEx_MI =~ emex1 + emex2 + emex3 + emex4 + emex5 + emex6 + emex7 + emex8 + emex9
'

mi_EmEx <- measurementInvariance(
  model = model_EmEx,
  data = data_clean,
  group = "LANGUAGE",
  estimator = "MLR",
  std.lv = TRUE,
  strict = FALSE
)

get_fit <- function(fit) {
  fitMeasures(fit, c("cfi", "rmsea"))
}

fit_table <- rbind(
  configural = get_fit(mi_EmEx$fit.configural),
  metric     = get_fit(mi_EmEx$fit.loadings),
  scalar     = get_fit(mi_EmEx$fit.intercepts)
)

fit_table

```

Germany - Canada: 
ΔCFI = -.0012   ΔRMSEA = -.0091 --> Metric invariance fulfilled 

ΔCFI = -.0313   ΔRMSEA = .0133 --> Scalar invariance not fulfilled

Germany - Canada - Taiwan: 
ΔCFI = −0.002   ΔRMSEA = −0.009 --> Metric invariance fulfilled 

ΔCFI = −0.031. ΔRMSEA = 0.013   --> Scalar invariance not fulfilled

## Invariance only for Dep
```{r}
model_Dep <- '
  Dep_MI =~ dep1 + dep2 + dep3 + dep4 + dep5 
'

mi_Dep <- measurementInvariance(
  model = model_Dep,
  data = data_clean,
  group = "LANGUAGE",
  estimator = "MLR",
  std.lv = TRUE,
  strict = TRUE   
)

get_fit <- function(fit) {
  fitMeasures(fit, c("cfi", "rmsea"))
}

fit_table <- rbind(
  configural = get_fit(mi_Dep$fit.configural),
  metric     = get_fit(mi_Dep$fit.loadings),
  scalar     = get_fit(mi_Dep$fit.intercepts)
)

fit_table

```

Germany - Canada: 

ΔCFI = -.0321   ΔRMSEA = .0076 --> Metric invariance not fulfilled 

ΔCFI = -.0237  ΔRMSEA = -.0021 --> Scalar invariance not fulfilled

Germany - Canada - Taiwan: 

ΔCFI = −0.032 ΔRMSEA = 0.008 --> Metric invariance not fulfilled 

ΔCFI = −0.023 ΔRMSEA = −0.002 --> Scalar invariance not fulfilled

